Urban Heat Risk Mapping Using Multiple Point Patterns in Houston, Texas

### 2016-08-18 jrssc-mpp.tex
Clarification of algorithm

%%% NOTE: STILL NEED TO DESCRIBE WHY IG PRIORS ARE APPROPRIATE %%%%
\textcolor{red}{Our approach for the remaining unknown parameters is to assume vague priors (and conjugate 
where possible). This is justified because there is sufficient data to learn these parameters without the need to rely heavily on prior information. We assume $\{\sigma^2_p\}$ and $\sigma^2_\mu$ are independent 
$\mathcal{IG}\left(2.001, 1.001\right)$ 
random variables where $\mathcal{IG}(a,b)$ denotes the inverse-gamma distribution with scale 
$a$ and rate $b$, a well-known conjugate prior for normal variance parameters. The $\mathcal{IG}(2.001, 1.001)$ distribution has a variance of 1000, providing sufficient flexibility for the data to accurately dictate the variances. For the regression coefficients we assume that $\boldsymbol{\beta} \sim 
\mathcal{N}(0, 50\mathbf{I}_{Q})$, leading to a Gaussian complete conditional for $\boldsymbol{\beta}$. 
Conjugate prior distributions for each spatial smoothness parameter (the $\nu$'s) and decay 
parameter (the $\psi$'s) are not available; however, following the results of \cite{Zhang2004}, 
a vague prior for the variance parameters (the $\sigma^2$'s) allows each smoothness and decay 
parameter to be fixed without loss generality or predictive power.}

\subsection{Model Fitting}
\textcolor{red}{We fit this model within a Bayesian framework. Because the priors
for $\boldsymbol{\alpha}_p$, $\boldsymbol{\gamma}_p$, and $\boldsymbol{\xi}_p$ are all conjugate, their posterior
distributions are known and can be drawn from directly. That is, we can easily obtain random draws from $\text{Dir}(n_{p,0} + 1, n_{p,1} + 1, \dots, n_{p,113})$, $\text{Dir}(n_{p,Female} + 1, n_{p,Male} + 1)$, and $\text{Dir}(n_{p,Asian} + 1, \dots, n_{p,White} + 1)$. The posterior densities for the rest of the parameters are unknown and so we obtain draws from the posterior using a Metropolis within Gibbs sampler of the following form:
\begin{enumerate}
  \item \label{draws2} Sample each $\sigma^2_p \sim [ \sigma^2_p | \boldsymbol{\phi}^\star_p, \mathbf{M}_p]$;
  \item \label{drawphi} Sample each $\phi^\star_p \sim [ \phi^\star_p | \sigma^2_p, \mathbf{M}_p ]$;
  \item \label{drawsmu} Sample $\sigma^2_\mu \sim [ \sigma^2_\mu | \boldsymbol{\mu}, \boldsymbol{\beta}, 
    \mathbf{M}_\mu ]$;
  \item \label{drawmu} Sample $\boldsymbol{\mu} \sim [ \boldsymbol{\mu} | \{\boldsymbol{\phi}^\star_p\}, 
    \{\sigma^2_p\}, \{\mathbf{M}_p\}, \sigma^2_\mu, \mathbf{M}_\mu, \boldsymbol{\beta} ]$; and
  \item \label{drawbeta} Sample $\boldsymbol{\beta} \sim [ \boldsymbol{\beta} | \boldsymbol{\mu}, 
    \sigma^2_\mu, \mathbf{M}_\mu ]$.
\end{enumerate}}

>>>>

\textcolor{red}{Our approach for the remaining unknown parameters is to assume vague priors (and conjugate 
where possible). %Is the following sentence sufficient to explain why we use vague priors?
This is justified because there is sufficient data to learn these parameters without the need to rely heavily on prior information. For $\delta_p$, we assume $\delta_p \sim \mathcal{G}(0.001, 0.001)$, where $\mathcal{G}(a,b)$ denotes the gamma distribution with shape $a$ and rate $b$. Note that for $\delta_p$ the likelihood in \eqref{likelihood} is proportional to $$\exp\left(-\delta_p\right)\delta_p^{n_p},$$ the kernel of a Poisson distribution. Therefore, the gamma prior for $\delta_p$ is conjugate, producing a posterior distribution of $\mathcal{G}(n_p + 0.001, 1 + 0.001)$. We assume $\{\sigma^2_p\}$ and $\sigma^2_\mu$ are independent 
$\mathcal{IG}\left(2.001, 1.001\right)$ 
random variables where $\mathcal{IG}(a,b)$ denotes the inverse-gamma distribution with scale 
$a$ and rate $b$, a well-known conjugate prior for normal variance parameters. The $\mathcal{IG}(2.001, 1.001)$ distribution has a variance of 1000, providing sufficient flexibility for the data to accurately dictate the variances. For the regression coefficients we assume that $\boldsymbol{\beta} \sim 
\mathcal{N}(0, 50\mathbf{I}_{Q})$, leading to a Gaussian complete conditional for $\boldsymbol{\beta}$. 
Conjugate prior distributions for each spatial smoothness parameter (the $\nu$'s) and decay 
parameter (the $\psi$'s) are not available; however, following the results of \cite{Zhang2004}, 
a vague prior for the variance parameters (the $\sigma^2$'s) allows each smoothness and decay 
parameter to be fixed without loss generality or predictive power.}

\subsection{Model Fitting}
\textcolor{red}{We fit this model within a Bayesian framework. For each health outcome $p = 1, \dots, P$, randomly generate draws for $\delta_p$ from the known posterior, $\mathcal{G}(n_p + 0.001, 1.001)$. Similarly, because the priors
for $\boldsymbol{\alpha}_p$, $\boldsymbol{\gamma}_p$, and $\boldsymbol{\xi}_p$ are all conjugate, their posterior
distributions are known and can be drawn from directly. That is, we can easily obtain random draws from $\text{Dir}(n_{p,0} + 1, n_{p,1} + 1, \dots, n_{p,113})$, $\text{Dir}(n_{p,Female} + 1, n_{p,Male} + 1)$, and $\text{Dir}(n_{p,Asian} + 1, \dots, n_{p,White} + 1)$, where as before $n_{p,0}$ denotes the number of people who experienced health outcome $p$ at age $0$, $n_{p,Female}$ indicates the number of females who experienced health outcome $p$, and so on.}

 \textcolor{red}{The posterior densities for the rest of the parameters are unknown and so we obtain draws from the posterior using a Metropolis within Gibbs sampler of the following form:
\begin{enumerate}
  \item \label{draws2} For $p = 1, \dots, P$, sample $\sigma^2_p \sim \mathcal{IG}(2.001 + \frac{K}{2}, 1.001 + \frac{1}{2}\boldsymbol\phi^{\star\prime}\mathbf{M}_p^{-1}\boldsymbol\phi^\star)$;%[ \sigma^2_p | \boldsymbol{\phi}^\star_p, \mathbf{M}_p]$;
  \item \label{drawphi} For $p = 1, \dots, P$, sample $\boldsymbol\phi^\star_p \sim [ \boldsymbol\phi^\star_p | \sigma^2_p, \mathbf{M}_p ]$;
  \item \label{drawsmu} Sample $\sigma^2_\mu \sim \mathcal{IG}(2.001 + \frac{K}{2}, 1.001 + \frac{1}{2}(\boldsymbol\mu - \mathbf{X}\boldsymbol\beta)^\prime\mathbf{M}^{-1}_\mu(\boldsymbol\mu - \mathbf{X}\boldsymbol\beta));$%[ \sigma^2_\mu | \boldsymbol{\mu}, \boldsymbol{\beta}, \mathbf{M}_\mu ]$;
  \item \label{drawmu} Sample $\boldsymbol{\mu} \sim [ \boldsymbol{\mu} | \{\boldsymbol{\phi}^\star_p\}, 
    \{\sigma^2_p\}, \{\mathbf{M}_p\}, \sigma^2_\mu, \mathbf{M}_\mu, \boldsymbol{\beta} ]$; and
  \item \label{drawbeta} Sample $\boldsymbol{\beta} \sim \mathcal{N}(\sigma_\mu^{-2}\Sigma^{\star}\mathbf{X}^\prime\mathbf{M}_\mu^{-1}\boldsymbol\mu, \Sigma^\star)$, where $\Sigma^\star = \left[\frac{1}{50}I_Q + \frac{1}{\sigma^2_\mu}\mathbf{X}^\prime \mathbf{M}_\mu^{-1}\mathbf{X}\right]^{-1}$.%[ \boldsymbol{\beta} | \boldsymbol{\mu}, \sigma^2_\mu, \mathbf{M}_\mu ]$.
\end{enumerate}}
